MSDi for all families together

### 2016-04-14 AllFamilys.Rmd
cambios 14/04/2016

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "sitio", ylab = "Theoretical ns = F", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsF.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
```

@@

```{r}
plot(nsT.theo.MSDi.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsT.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
```

>>>>

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical NS = F", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
```

@@

```{r}
plot(nsT.theo.MSDi.s, type="l", xlab = "sitie", ylab = "Theoretical NS = T", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", xlab = "sitie", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsT.theo.MSDi.s, type = "l", xlab = "sitie", ylab = "Merge", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
```

### 2016-04-14 INFORMATION/paper.tex
cambios 14/04/2016

\documentclass{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

@@

\section{Introduction}
Proteins diverge during biological evolution, which is evident in the variation of the aminoacid sequences and the resulting structural, dynamical and functional changes. It is known that the structure diverges much more slowly than the sequence and that the  structural divergence occurs mainly along the lower energy vibrational modes of proteins and that there are structurally conserved ``cores'' in families of proteins [1]. These facts are difficult to interpret because most of the studies that have been made are purely empirical. To go forward in this sense, it has been developed the mechanistic model ``Linearly Forced – Elastic Network Model'' (LF - ENM), which predicts the change in the equilibrium position of the sites as a result of random mutations, not subjected to natural selection. Applying this model, it was shown that the patterns of structural change (greater contribution of lower energy normal modes and the existence of a structurally conserved ``core'') can be predicted without resorting to natural selection [3,4]. With regard to the dynamics, this model reproduces well the observed pattern that the normal modes of lower energy are more evolutionarily conserved, even in the absence of natural selection [5]. This implies that such modes are more robust to random mutations, so that they would conserve more even in the absence of natural selection. All these results call into question interpretations based on the assumption that everything that is conserved or that varies is related to the biological function.
While natural selection apparently little affects structural and dynamical divergence patterns, at the level of aminoacid sequences, different sites evolve at different speeds. Purely mutational evolutional models such as the LF-ENM, cannot account for this fact. To explain such patterns of sequence variation, natural selection must be modeled. Recently, we have proposed a mechanistic model (``Stress Model'') in which a mutation is accepted at a rate proportional to the probability that the mutant adopts the ``active structure". This model has been used to account for the average evolutionary variation from site to site [6].
As we said, the LF-ENM model has been successfully used to explain the observed patterns of structural and dynamical divergence in the absence of natural selection. However, it is expected that the selection restricts the structural divergence and / or dynamics. For example if the structure and fluctuations of an enzyme`s active site are important for enzymatic activity, one would expect that the structure and movements are evolutionarily conserved significantly higher than expected for purely mutational patterns. Therefore, no matter how weak, some evidence of natural selection at the level of structural and dynamical divergence would be expected. The aim of this work is to find evidence of natural selection at the structural divergence level.

@@

\begin{equation}
d\mathbf{r}^{tot} = d\mathbf{r}^{mut1}_{wt}+d\mathbf{r}^{mut2}_{wt}+ ...+d\mathbf{r}^{mutm}_{wt}+...+d\mathbf{r}^{mutNmut}_{wt}
\end{equation}

\begin{equation}
d\mathbf{r}^{tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{fmut}_{Nmut}) 
\end{equation}

Where $d\mathbf{r}^{tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}^{wt}$), and $\mathbf{fmutm}$ is the vector of force of the $m$ mutation.

@@

{\it Mutants without natural selection (NS = F):} For family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites. For each of these pairs, we generated 10 mutants. Hence, again, if the family has $P$ proteins plus the reference protein, we obtained a simulated dataset of  $10 \times P$  members.

@@

\begin{equation}
\left\|d\mathbf{r}^{0}_{i}\right\|^{2}=d\mathbf{x}^{0}_{i}^{2}+d\mathbf{y}^{0}_{i}^{2}+d\mathbf{z}^{0}_{i}^{2}
\end{equation}

Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $ith$ $C_{\alpha}$ with respect to the reference structure obtained from Eq. (4). To diminish noisy information, we smoothed these profiles as shown:

@@

{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x M profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID. Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles. Finally, we calculated the average of averages and the average of quantiles. 
For the experimental dataset, the average and 0.05 and 0.95 quantile profiles of each family were calculated.

@@

{\it Normal modes coordinates:}
In order to analyze the effect of natural selection on the structural variability projected onto normal modes coordinates of the reference protein, we obtained average $P_{n}$ profiles and 0.05 and 0.95 quantiles profiles as explained in Methods. To compare the experimental dataset with the theoretical datasets we calculated the $R^2$ and the $MSE$ between them. The results are shown in Table 2 and figure 3. Table 1 and figure 2 show that, again, the $R^2$ between experimental data and theoretical data, with or without natural selection, is high, $\approx 0.7$ and that natural selection does not seem to improve the agreement with experimental data.

\section{Conclusion}

>>>>

\documentclass{article}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{multicol}

@@

\begin{multicols}{2} 
\section{Introduction}
Proteins diverge during biological evolution, which is evident in the variation of the aminoacid sequences and the resulting structural, dynamical and functional changes. It is known that the structure diverges much more slowly than the sequence and that the  structural divergence occurs mainly along the lower energy vibrational modes of proteins and that there are structurally conserved ``cores'' in families of proteins [1]. These facts are difficult to interpret because most of the studies that have been made are purely empirical. To go forward in this sense, it has been developed the mechanistic model ``Linearly Forced – Elastic Network Model'' (LF - ENM), which predicts the change in the equilibrium position of the sites as a result of random mutations, not subjected to natural selection. Applying this model, it was shown that the patterns of structural change (greater contribution of lower energy normal modes and the existence of a structurally conserved ``core'') can be predicted without resorting to natural selection [3,4]. With regard to the dynamics, this model reproduces well the observed pattern that the normal modes of lower energy are more evolutionarily conserved, even in the absence of natural selection [5]. This implies that such modes are more robust to random mutations, so that they would conserve more even in the absence of natural selection. All these results call into question interpretations based on the assumption that everything that is conserved or that varies is related to the biological function.
While natural selection apparently little affects structural and dynamical divergence patterns, at the level of aminoacid sequences, different sites evolve at different speeds. Purely mutational evolutional models such as the LF-ENM, cannot account for this fact. To explain such patterns of sequence variation, natural selection must be modeled. Recently, we have proposed a mechanistic model (``Stress Model'') in which a mutation is accepted at a rate proportional to the probability that the mutant adopts the ``active structure". This model has been used to account for the average evolutionary variation from site to site [6].
As we said, the LF-ENM model has been successfully used to explain the observed patterns of structural and dynamical divergence in the absence of natural selection. However, it is expected that the selection restricts the structural divergence and / or dynamics. For example if the structure and fluctuations of an enzyme`s active site are important for enzymatic activity, one would expect that the structure and movements are evolutionarily conserved significantly higher than expected for purely mutational patterns. Therefore, no matter how weak, some evidence of natural selection at the level of structural and dynamical divergence would be expected. The aim of this work is to find evidence of natural selection at the structural divergence level.

@@

\begin{equation}
d\mathbf{r}^{0,tot} = d\mathbf{r}^{0,mut1}_{wt}+d\mathbf{r}^{0,mut2}_{wt}+ ...+d\mathbf{r}^{0,mutm}_{wt}+...+d\mathbf{r}^{0,mutNmut}_{wt}
\end{equation}

\begin{equation}
d\mathbf{r}^{0,tot} =\mathbf{K}^{-1}_{wt}\times(\mathbf{f}_{mut1}+\mathbf{f}_{mut2}+...+\mathbf{f}_{mutm}+...+\mathbf{f}_{mutNmut}) 
\end{equation}

Where $d\mathbf{r}^{0,tot}$ is the total structural variation due the M mutations, $d\mathbf{r}^{0,mutm}_{wt}$ is the structural variation produced by the mutation $m$ (considering $\mathbf{K}_{wt}$), and $\mathbf{f}_mutm}$ is the vector of force of the $m$ mutation.

@@

{\it Mutants without natural selection (NS = F):} For each family and for each pair comprising the reference protein and one of the other proteins of the family, we obtained the number of sites to mutate as mentioned before and we mutated randomly this number of sites. For each of these pairs, we generated 10 mutants. Hence, again, if the family has $P$ proteins (plus the reference protein), we obtained a simulated dataset of  $10 \times P$  members.

@@

\begin{equation}
\left\|d\mathbf{r}^{0}_{i}\right\|^{2}=dx^{0,2}_{i}+dy^{0,2}_{i}+dz^{0,2}_{i}
\end{equation}

Were $d\mathbf{r}^{0}_{i}=(d\mathbf{x}^{0}_{i}d\mathbf{y}^{0}_{i}d\mathbf{z}^{0}_{i})^{T}$ is the column vector of cartesian displacements of the $i^{th}$ $C_{\alpha}$ with respect to the reference structure obtained from Eq. (4). To diminish noisy information, we smoothed these profiles as shown:

@@

{\it Normal modes coordinates:} For the theoretical datasets, with or without natural selection, the 10 x P profiles of $P_{n}$ of each family were split in 10 groups so that in all of them there was a simulated mutant that corresponded to an experimental pair of proteins of the family in means of the \% ID. Then we calculated, for these 10 groups, the average and 0.05 and 0.95 quantiles. Finally, we calculated the average of averages and the average of quantiles. 
For the experimental dataset, the average and 0.05 and 0.95 quantile profiles of each family were calculated.

@@

{\it Normal modes coordinates:}
In order to analyze the effect of natural selection on the structural variability projected onto normal modes coordinates of the reference protein, we obtained average $P_{n}$ profiles and 0.05 and 0.95 quantiles profiles as explained in Methods. To compare the experimental dataset with the theoretical datasets we calculated the $R^2$ and the $MSE$ between them. The results are shown in Table 2 and figure 2. Table 1 and figure 2 show that, again, the $R^2$ between experimental data and theoretical data, with or without natural selection, is high, $\approx 0.7$ and that natural selection does not seem to improve the agreement with experimental data.

\section{Conclusion}
\end{multicols}

### 2016-04-14 figure_1.Rmd
cambios 14/04/2016

---
title: "MSDi for all families together"
author: "Maria Laura Marcos"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

@@

# Create matrixes.
nsF.theo.MSDi = c()
nsT.theo.MSDi = c()
nsF.theo.MSDi.s = c()
nsT.theo.MSDi.s = c()

exp.MSDi = c()
exp.MSDi.s = c()

@@

# Print the input in the html file.
print(input)

@@

  m.cF.exp.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.dr.squarei.csv", sep = "")))
  m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))

  cF.exp.MSDi = colMeans(m.cF.exp.dr.squarei, na.rm = T )
  cF.exp.MSDi.s = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )

  #Read theoretical data#

  # natural selection (ns) = F.
  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

  # natural selection (ns) = T.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)

  ## Fit theoretical data with experimental data.
  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
  fit.nsF.cF.MSDi = fitted.values(fit.nsF.cF)

  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
  fit.nsT.cF.MSDi = fitted.values(fit.nsT.cF)

@@

  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)

  # Concatenate information.
  nsF.theo.MSDi = c(nsF.theo.MSDi, fit.nsF.cF.MSDi)
  nsT.theo.MSDi = c(nsT.theo.MSDi, fit.nsT.cF.MSDi)
  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)

  cF.exp.MSDi = cF.exp.MSDi[!is.na(cF.exp.MSDi)]
  cF.exp.MSDi.s = cF.exp.MSDi.s[!is.na(cF.exp.MSDi.s)]

  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
}

# Caluclate measures.
R2.nsF.cF = cor(nsF.theo.MSDi, exp.MSDi) ^ 2 
R2.nsT.cF = cor(nsT.theo.MSDi, exp.MSDi) ^ 2

R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2

MSE.nsF.cF = mean((nsF.theo.MSDi - exp.MSDi) ^ 2)
MSE.nsT.cF = mean((nsT.theo.MSDi - exp.MSDi) ^ 2)

MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)

@@

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F))

plot(nsF.theo.MSDi, type = "l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type = "l", col = "red", ylab = "Experimental")
plot(nsF.theo.MSDi, type = "l", ylab = "both")
points(exp.MSDi, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(nsT.theo.MSDi, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(nsT.theo.MSDi, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
```
All families fitted smooth normalized MSD profiles

Without natural selection (ns = F)

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical NS = F", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental", ylim = c(0, 0.14))
```

@@

With natural selection (ns = T)

```{r}
plot(nsT.theo.MSDi.s, type="l", xlab = "sitie", ylab = "Theoretical NS = T", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", xlab = "sitie", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsT.theo.MSDi.s, type = "l", xlab = "sitie", ylab = "Merge", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
```

>>>>

---
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

@@

nsF.theo.MSDi.s = c()
exp.MSDi.s = c()

@@

@@

  m.cF.exp.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.dr.squarei.csv", sep = "")))

  cF.exp.MSDi.s = colMeans(m.cF.exp.smooth.dr.squarei, na.rm = T )

  #Read theoretical data#
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

  ## Fit theoretical data with experimental data.

@@

  # Concatenate information.

  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)

  cF.exp.MSDi.s = cF.exp.MSDi.s[!is.na(cF.exp.MSDi.s)]
  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
}

# Caluclate measures.

R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2

MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)

@@

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = F", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", xlab = "site",  ylab = "Experimental MSDi ", ylim = c(0, 0.14))
```

@@

### 2016-04-14 figure_2.Rmd
cambios 14/04/2016

nsF.theo.MSDi.s = c()
exp.MSDi.s = c()

@@

  #Read experimental data.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "FALSE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

@@

  #Read theoretical data#
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

@@

  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.MSDi.s)
  fit.nsF.cF.MSDi.s = fitted.values(fit.nsF.cF.s)

@@

  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)

@@

R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2

MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)

@@

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = F", ylim = c(0, 0.14))
```

@@

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
```

>>>>

nsT.theo.MSDi.s = c()
exp.MSDi.s = c()

@@

  #Read experimental data.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

@@

  #Read theoretical data#
  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)

@@

  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)

@@

  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)

@@

R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2

MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)

@@

```{r}
plot(nsT.theo.MSDi.s, type = "l", xlab = "site", ylab = "Theoretical MSDi NS = T", ylim = c(0, 0.14))
```

@@

```{r}
plot(nsT.theo.MSDi.s, type = "l", xlab = "site", ylab = "Merge", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 4)), bty = "n", text.col = "red")
```
